\section{Related Work}
\label{sec:related}

As mentioned earlier, much of our work was inspired by FortNox. Although, there have been other approaches to security in software defined networks as well.

Ethane \cite{Casado:2007:ETC:1282380.1282382} was a predecessor and driving force behind the development of software defined networking as we see it today.
It was born out of the need to be able to manage and enforce fine-grained policies across an entire network.
The design of Ethane consists of a central controller and dumb switches, which are the building blocks of SDN today.
This system was designed with security in mind since enforcing security in an enterprise network is essentially a set of policies that need to be managed across the entire network.
Ethane provides ease of management for network policies, but it does not address how a controller is to protect against conflicting policies introduced by administrators and third party applications.

FlowVisor \cite{flowvisor} allows for a single physical network to be divided into logical "slices."
Each slice received its own controller and therefore runs its own set of application of the controller.
This provides isolation between the different applications and guarantees that they do not misbehave with each other.
While this is desirable, it is not practical to expect an enterprise to create a new network slice, and thus a new controller, for every third party application.
The management of these different entities could get very complicated very quickly.
Also, FlowVisor does not provide any security within a slice.
Therefore, if there is a need to run several applications on the same network slice, there is no guarantee that they will cooperate with each other.

%Our work is based off of FortNOX \cite{Porras:2012:SEK:2342441.2342466}, a security enforcement kernel for the NOX OpenFlow Controller \cite{Gude:2008:NTO:1384609.1384625}.
%FortNOX provides role-based authorization and security constraint enforcement for applications running on the controller.
%They proposed reducing flow rules into alias reduced rules which are then compared to detect conflicts.
%We created our own version of alias reduced rules within the confines of how Floodlight represents flow rules.
